Minimizing post-shock forecasting error using disparate information

### 2020-06-14 manuscript/manuscript.tex
major revision to discussion, and minor edits to abstract, introduction, methodology, data analysis, and simulation

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction. Bootstrap procedures are provided to estimate the variability of our shock effect estimators and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. The risk-reduction conditions are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap. These propositions are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well, using estimates from bootstrap procedures. Our simulation results show that the proposed bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

@@

 These are some analytical results for comparison studies among estimators of $\alpha_1$. Next, we will detail a framework for estimation of risk-reduction  quantities using a parametric bootstrap routine. Therefore, the above inequalities can be analyzed numerically in practice.

@@

In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, and checks the underlying conditions of our risk reduction results in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement and the other without any resampling of the donor pool. We denote them by $\mc{B}_1$ and  $\mc{B}_2$, respectively. We first illustrate the simple $\mc{B}_2$. The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool. Initialize $y_{i,0}$ for all $i \in I$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
One can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

$\mc{B}_1$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$. Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$.

@@

$\mc{B}_1$ takes the perspective of treating the donor-pool candidates to be random while $\mc{B}_2$ takes them as fixed. Therefore, it is possible that $\mc{B}_1$ can improve precision of $\mc{B}_2$.  Notice that $\mathbf{W}^*$ is random in $\mc{B}_1$. It is likely that  $\mc{B}_1$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ since $\mathbf{W}^*$ may possibly take values on the boundary of the parameter space \citep{andrews2000inconsistency}. For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$. The subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$ and $m/n \to 0$ as $n \to \infty$. However, we may leave its mathematical justification for future research. Note that this problem will not occur under  $\mc{B}_2$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.

Let 
$
  \overline{\hat{\alpha}_{\mrm{adj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because its weights are random. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We would only claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_2$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$. %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population. For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$. 
For $\mc{B}_1$ but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold. Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.

@@

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\gamma}= \sigma_{\delta}=\sigma_{\alpha} \in  \{0.01, 0.1, 1, 10\}$ where we fix $\sigma$ to 1. The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown. It is shown in Table ? that as the donor pool size increases, the bias and consistency results improve with more precision. In contrast, the result gets poorer as  the variance of $\alpha_i$ increases. It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$. Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates. But it is reversed in the random design case.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an RMSE of 19.680 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $4.441$, and $4.423$ dollars, respectively.
Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. However, the risk-reduction quantities are inconsistent with the reality. The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.

@@

\section{Discussion}

@@

Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series. The pseudo time series generated by parametric bootstrap is not stationary. Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$. This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$. The sampling stops when $N$ observations are reached. Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d. discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d. geometric random variables with parameter $p$.  However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$. This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}. It is up to the user in selecting which procedure to choose but under different assumptions on the time series.

For the use of our methodology, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest. We recommend using $\mc{B}_1$ when the donor pool size $n$ is large, and $\mc{B}_2$ when $n$ is small.

>>>>

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. The risk-reduction conditions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap. These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best, using estimates from bootstrap procedures. Our Monte Carlo simulation results show that  the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

@@

 These are some analytical results for comparison studies among estimators of $\alpha_1$. Next, we will detail a framework for estimation of risk-reduction  quantities using a parametric bootstrap routine. Therefore, the above inequalities can be analyzed numerically and risk-reduction quantities can be estimated using plug-in estimators in practice.

@@

In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction results, and estimate risk-reduction using plug-in approach in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement (\emph{unconditional} on donor pool) and the other without any resampling of the donor pool (\emph{conditional} on donor pool). We denote them by $\mc{B}_u$ and  $\mc{B}_c$, respectively. We first illustrate the simple $\mc{B}_c$. The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool. Initialize $y_{i,0}$ for all $i \in I$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
One can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

$\mc{B}_u$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$. Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$. We would assume $\mathbf{W}^*$ is non-degenerate (i.e., no zero weights) in the population when using $\mc{B}_u$.  See Section \ref{discussion} for discussions.

@@

Now, we discuss some consistency results for $\mc{B}_c$ conditioned on $\Theta_1$. Let 
$
  \overline{\hat{\alpha}_{\mrm{adj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because its weights are random. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We would only claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_c$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$. %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population. For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$. 
For $\mc{B}_u$ but conditioned on $\Theta$, we emphasize that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold. Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.

@@

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\gamma}= \sigma_{\delta}=\sigma_{\alpha} \in  \{0.01, 0.1, 1, 10\}$ where we fix $\sigma$ to 1. The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown. It is shown in Table ? that as the donor pool size increases, the bias and consistency results improve with more precision. In contrast, the result gets poorer as  the variance of $\alpha_i$ increases. It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$. Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates. But it is reversed in the random design case. Moreover, notice that the consistency for voting the best estimator works poor when $n$ is small but improves significantly when $n$ is large.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an RMSE of 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $4.441$, and $4.423$ dollars, respectively.
Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. However, the risk-reduction quantities are inconsistent with the reality. The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.  It is consistent with the finding in Section \ref{parametricbootstrapsimulation} that voting for best estimator with estimated risk-reduction quantities is very likely to be inconsistent with the truth when the donor pool size $n$ is small.

@@

\section{Discussion}
\label{discussion}

@@

Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series. The pseudo time series generated by parametric bootstrap is not stationary. Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$. This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$. The sampling stops when $N$ observations are reached. Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d. discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d. geometric random variables with parameter $p$.  However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$. This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}. It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.

In terms of the use of our bootstrap procedure, we caution that the bootstrapping residuals in OLS estimation may not provide valid inference in high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}. Recall that in Section \ref{varbootstrap}, we proposed two possible bootstrap procedures, $\mc{B}_u$  and $\mc{B}_c$. There are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_c$. $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors. In contrast $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error. Therefore, it is possible that $\mc{B}_u$ can improve precision of $\mc{B}_2$. In this study, for the use of $\mc{B}_u$, we assume $\mathbf{W}^*$ is non-degenerate in the population with taking zero weight. However, it is likely that $\mathbf{W}^*$ may possibly take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}. For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$. In this regard, the subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$. But we may leave its mathematical justification for future research. Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$. That being said, if in practice users detect the boundary case (e.g., $\mathbf{W}^*$ in Section \ref{forecasting}), they are not recommended to use $\mc{B}_u$. Besides, we  recommend using $\mc{B}_c$ when the donor pool size $n$ is small. When $n$ is large, the selection would be more up to how users think of the philosophical differences between $\mc{B}_u$ and $\mc{B}_c$ up to application of interest, and the problems that  $\mc{B}_u$ may fail.

For the use of our methodology, caution should be dedicated to the construction of donor pool. If the donor pool includes some individuals that are not similar to the time series of interest, the result will possibly not be robust to the introduced noises.   Additionally, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large. It is  due to the fact that plug-in estimation of  risk-reduction quantities gains more precision when $n$ becomes large.
